### 2015-04-10 implementation.tex
Minor edit.

Each effect generated as a result of an effectful operation on an object
inserts a new row $(o,\allowbreak e,\allowbreak txn,\allowbreak val,
\allowbreak deps)$ into the backing store, where $o$ and $e$ are object and
\emph{unique} effect identifiers, $txn$ is an optional transaction identifier,
and $val$ is the value associated with the effect (eg: \cf{Withdraw 50}).
$deps$ is the set of identifiers of \emph{dependencies} of this operation and
is defined as $deps(e) = \{e_1 \ALT \vis{e_1}{e} \wedge \neg(\exists
e_2.\vis{e_1}{e_2} \wedge \vis{e_2}{e})\}$. At any shim layer node, an effect
is included only if all of its dependencies are also included in that node.
This ensures that the state maintained by the shim layer node is causally
consistent. Our dependence tracking strategy ensures that \name does not track
every effect as the number of writes in the system grows.

@@

\name implements atomic visibility by exploiting shim layer causality guarantees
-- an effect is included only if all the effects if depends on are also
included. Consider the example given in Figure~\ref{fig:atomicity_impl}. For
every transaction in \name, we instantiate a special transaction marker
effect $m$ that is importantly not inserted into the backing store. Marker $m$ is
included as a dependence to every effect generated in the transaction. In the
figure, the top graph on the left shows the state of the store in the middle of a
transaction. Each circle represents an effect. The dotted circle indicates that
the effect has been instantiated, but has not yet been inserted into the store.
Since the causally preceding effect $m$ has not yet been written to the store,
no operation will witness $e1$ and $e2$ while the transaction in progress.
After the transaction has finished execution, we insert $m$ into the backing
store, marking all the effects from the transactions as a dependence for $m$.
Now, any replica which includes one of the effects from the transaction must
include $m$, and transitively must include every effect from the transaction.
This ensures atomicity and satisfies the RC requirement.

>>>>

Each effect generated as a result of an effectful operation on an object
inserts a new row $(o,\allowbreak e,\allowbreak txn,\allowbreak val,
\allowbreak deps)$ into the backing store, where $o$ and $e$ are object and
\emph{unique} effect identifiers, $txn$ is an optional transaction identifier,
and $val$ is the value associated with the effect (eg: \cf{Withdraw 50}).
$deps$ is the set of identifiers of \emph{dependencies} of this operation and
is defined as $deps(e) = \{e_1 \ALT \vis{e_1}{e} \wedge \neg(\exists
e_2.\vis{e_1}{e_2} \wedge \vis{e_2}{e})\}$. At any shim layer node, an effect
is included only if all of its dependencies are also included in that node.
This ensures that the state maintained by the shim layer node is causally
consistent. Hence, our dependence tracking strategy ensures that \name does not
track every effect as the number of writes in the system grows.

@@

\name implements atomic visibility by exploiting shim layer causality guarantees
-- an effect is included only if all the effects if depends on are also
included. Consider the example given in Figure~\ref{fig:atomicity_impl}. For
every transaction in \name, we instantiate a special transaction marker effect
$m$ that is importantly not inserted into the backing store. Marker $m$ is
included as a dependence to every effect generated in the transaction. In the
figure, the top graph on the left shows the state of the store in the middle of
a transaction. Each circle represents an effect. The dotted circle indicates
that the effect has been instantiated, but has not yet been inserted into the
store. Since the causally preceding effect $m$ has not yet been written to the
store, no operation will witness $e1$ and $e2$ while the transaction in
progress. After the transaction has finished execution, we insert $m$ into the
backing store, marking all the effects from the transactions as a dependence
for $m$, as show in the bottom graph. Now, any replica which includes one of
the effects from the transaction must include $m$, and transitively must
include every effect from the transaction. This ensures atomicity and satisfies
the RC requirement.
